Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:06	23:37:16	(Tue 6.Oct)

From this we hypothesize that LCA should work even if it only selects from various Kaiser windows. If they span a decent range of $\beta$-values, and some steering variations is applied to each, we should have responses that resembles those in \Fig{mvdr_selected_windows}. The Kaiser window is easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian. It is also optimal in the sense of having its peak power concentration near the steering angle.

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions with an even worse white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.

\mediaII{} shows how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$ and temporal averaging $K$. It demonstrates that at $L=1$ the window responses are rectangular in all areas in the image. At $L=2$ we can observe that pixels in highlight are processed with windows with slightly varying amplitude responses, but with the phase being 0$^\circ$ in the illuminated seafloor sector. Yet MVDR is able to greatly suppress noise, which seems to emphasize the importance varying the zero locations slightly to suppress noise. The media file also shows MVDR can be run with subarray sizes $L\in[M/2,5M/8]$, but only with temporal averaging $K=1$ or above.

@@

What is the best set of Kaiser windows to use with LCA, and how much should they be steered? To investigate this we constructed large and equally sized window databases containing windows with varied upper boundaries for $\beta$ and $\phi$. As lower boundaries we chose $\beta=0$ and $\phi=0^\circ$, which includes the symmetric rectangularly weighted DAS image. The images produced are shown in \Fig{oversampling_mosaic_bounds}. In each image we computed the lateral distance $\Delta x$ between the -3dB points of the anchor, with the reference $\Delta x_\text{ref}$ being the rectangularly weighted DAS image. A forth order polynomial fit was used in this computation. This measure is also commonly called the full width half maximum (FWHM). In the case of a imaging a point scatter, it is closely related to the resolution of of the system. For a rectangular window, for instance, the system resolution is approximately $\Delta \approx \text{FWHM}/0.89$~\cite{Harris1978}.

>>>>

From this we hypothesize that a good window database LCA can be made using a varied  set of Kaiser windows. If they span a suitable range of $\beta$-values, and some steering variations are applied to each, we should have responses that resemble those in \Fig{mvdr_selected_windows}. The Kaiser window is easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian. It is also optimal in the sense of having its peak power concentration near the steering angle.

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from inverted Kaiser windows. These have a mainlobe width narrower than that of the rectangular window, but at the expense of a very poor white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions of them. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of \minus{}13\,dB.

\mediaII{} animates how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$ and temporal averaging $K$. At $L=1$ the window responses are rectangular in all areas in the image. At $L=2$ we observe window responses with slight amplitude variations in the highlight region, but with the phase being 0$^\circ$ in the illuminated seafloor sector. Already at $L=2$ the MVDR is able to greatly suppress noise. This is a common observation; adding a little flexibility to adapt to the scene has a dramatic effect, but further allowing full flexibility is much less significant. The media file also shows that MVDR can be run with subarray sizes $L\in[M/2,5M/8]$, but only with temporal averaging $K=1$ or above.

@@

To determine a suitable range for the Kaiser parameter $\beta$ and steering $\phi$, we constructed large and equally sized window databases containing Kaiser windows with varied upper boundaries for $\beta$ and $\phi$. The lower boundaries were chosen as $\beta=0$ and $\phi=0^\circ$, which includes the rectangularly weighted DAS image. The resulting images are shown in \Fig{oversampling_mosaic_bounds}. In each image we computed the lateral distance $\Delta x$ between the \minus{}3dB points of the anchor, with the reference $\Delta x_\text{ref}$ being the rectangularly weighted DAS image. A forth order polynomial fit was used in this computation. This measure is also commonly called the full width half maximum (FWHM). In the case of a imaging a point scatter, it is closely related to the resolution of of the system. For a rectangular window, for instance, the system resolution is approximately $\Delta \approx \text{FWHM}/0.89$~\cite{Harris1978}.
